WORCS: A Workflow for Open Reproducible Code in Science

### 2020-10-28 paper/Manuscript_DS.Rmd
Tweak docker references

Many solutions exist to ensure computational reproducibility, which differ in
user-friendliness and effectiveness. 
These solutions typically work by
enveloping your research project in a distinct "environment" that only has access to programs that
are explicitly installed, and maintaining a record of these programs.
If strict reproducibility is required, users might choose to conduct all analyses in a "Docker container": An environment that behaves like a
virtual computer, which can be stored like a time capsule, and
identically reinstated on a user computer, or in the cloud.
This is effective, and also preserves software outside the `R` environment (e.g.,
preprocessing tools for neuroimaging data). A Docker-based workflow
that is conceptually and practically compatible with WORCS
was recently introduced by @peikertReproducibleDataAnalysis2019.
However, it is somewhat difficult to set up for novice users. 
The `R` package `repro`
is currently in development to facilitate adoption [@repro]. 
Another 
user-friendly Docker-based workflow is offered by the cloud-based collaboration
platform 'Code Ocean'. Although Code Ocean enjoys some popularity among 
scientists, it is not clear whether this platform
is GDPR compliant - as of this writing, its [terms of use](https://codeocean.com/terms-of-use) do not address the GDPR, nor is it clear where
data are stored.
The necessity to upload human participant data is a liability
when using any
cloud-computing solution for data analysis.

>>>>

Many solutions exist to ensure computational reproducibility, which differ in
user-friendliness and effectiveness. 
These solutions typically work by
enveloping your research project in a distinct "environment" that only has access to programs that
are explicitly installed, and maintaining a record of these programs.
If strict reproducibility is required, users might choose to conduct all analyses in a "Docker container": An environment that behaves like a
virtual computer, which can be stored like a time capsule, and
identically reinstated on a user computer, or in the cloud.
This is effective, and also preserves software outside the `R` environment (e.g.,
preprocessing tools for neuroimaging data).
The [stetup with Docker vignette](https://cjvanlissa.github.io/worcs/articles/docker.html)
describes how users may instantiate a Docker build running `worcs` and its dependencies.
For more information on this topic,
@peikertReproducibleDataAnalysis2019 describe 
a Docker-based workflow for computational reproducibility that is
conceptually and practically compatible with WORCS.
One remaining challenge of Docker is that it is somewhat difficult to set up for novice users.
The `worcs` package meets most reproducibility requirements while using only tools
native to RStudio, and is therefore easier to adopt for `R` users.
However, an `R` package is currently in development to facilitate Docker integration [`repro`, @repro].
Another 
user-friendly Docker-based workflow is offered by the cloud-based collaboration
platform 'Code Ocean'. Although Code Ocean enjoys some popularity among 
scientists, it is not clear whether this platform
is GDPR compliant - as of this writing, its [terms of use](https://codeocean.com/terms-of-use) do not address the GDPR, nor is it clear where
data are stored.
The necessity to upload human participant data is a liability
when using any
cloud-computing solution for data analysis.
